Estimating contemporary migration rates of adults for iteroparous species using kinship pairs found between populations

### 2022-01-24 latex/ms.tex
add somethings
change title
add memo in Intro

\title{Estimating contemporary migration rates for iteroparous species using kinship pairs found between populations}
\author{
Tetsuya Akita$^{a}$\thanks{
\emph{Corresponding author}:
    Fisheries Resources Institute, Fisheries Research and Education Agency, Kanagawa 236-8648, Japan.
    E-mail: akitatetsuya1981@affrc.go.jp} \\ 
   \small $^{a}$Fisheries Resources Institute, Fisheries Research and Education Agency, \\
   \small Kanagawa, 236-8648, Japan.
   }
\date{Manuscript Intended for \emph{Methods in Ecology and Evolution}, \today}
\maketitle

@@

Estimating the number of migrants among the populations is essential for understanding population structure and dynamics, which is a fundamental process for implementing conservation and wildlife management. Especially in fisheries management, migration rate is a critical component for delineating a synchrony among the population, providing appropriate management units. There are essentially two approaches for estimating the migrant number. The first is to use the mark-recapture method estimate it directly from the population dynamics modeling with survey data. The second is to ...

@@

%conn & bravington も引用しないと
% MigEst by Wangとの比較も...

%Caveat: selectivity, family correlated migration、skip spawning,

>>>>

\title{Estimating contemporary migration rates of adults for iteroparous species using kinship pairs found between populations}
\author{
Tetsuya Akita$^{a}$\thanks{
\emph{Corresponding author}:
    Fisheries Resources Institute, Fisheries Research and Education Agency, Kanagawa 236-8648, Japan.
    E-mail: akitatetsuya1981@affrc.go.jp} \\ 
   \small $^{a}$Fisheries Resources Institute, Fisheries Research and Education Agency, \\
   \small Kanagawa, 236-8648, Japan.
   }
\date{Manuscript Intended for \emph{Methods in Ecology and Evolution}, \today}
\maketitle

@@

%conn & bravington も引用しないと
% MigEst by Wangとの比較も...もう一度よくWang 2014を読む！どうやって推定しているのか...
%% 今回提案した方法は、ゴーストポップがあっても大丈夫
%% MigEstは、親は動かず、子が移動することを想定している
%% N = Neを想定

%移動には２種類ある。子の移動と親の移動である。前者は花粉やラーバなど。connectivityは前者が大事かもで、どこまで遠く行くのかも重要。移動する生物の場合、後者も重要。

Estimating the number of migrants among the populations is essential for understanding population structure and dynamics.

, which is a fundamental process for implementing conservation and wildlife management. Especially in fisheries management, migration rate is a critical component for delineating a synchrony among the population, providing appropriate management units.

% 近年の移動率の推定には大きく２種類に分類される。１つ目は遺伝マーカーに基づく集団遺伝学的な解析。２つ目は標識採捕の枠組みの解析。

There are essentially two approaches for estimating the migrant number. The first is to use the mark-recapture method estimate it directly from the population dynamics modeling with survey data. The second is to ...

@@

%PRE-DEFINED population !
%Caveat: selectivity, family correlated migration、skip spawning,
